Chapter 2

\chapter{Instrumentation} % Write in your own chapter title
\label{chap:ins}
\lhead{Chapter 2. \emph{Instrumentation}} % Write in your own chapter title to set the page header

AGN are found in surveys in X and then we look for counterparts in the optical.

\section{X-ray observations}
\label{sec2:xr}


\subsection{XMM-Newton}
\label{sec2:xmm}
Information about the XMM-newton cameras and how the X-ray data are processed from the incoming radiation to the files (the post processing of the extraction of the sources and modeling of the spectra is not in this section)



\section{Ground based telescopes}
\label{sec2:tel}

For the optical observations of the sources. In order to identify all the X-ray sources, optical observations are made. Some of the optical counterparts comes from the SDSS public archive. Others are made using follow up observations.



\subsection{Long Slit spectra from optical telescopes}
\label{sec2:otel}

Describe each telescope and where is located. After that describe the instrument, wavelength coverage.

VLT/XSHOOTER

Description about the XSHOOTER instrument, how the uv-to-nir radiation is divided and mention the echelle grating. Mention as well the ADC in this section. From the pipeline and reduction is in the following chapter. Maybe this section should be included in the optical telescopes.

GTC/OSIRIS

TNG/DOLORES

VLT/FORS2

WHT/ISIS

WHT/ACAM

NTT/EFOSC

NOT/ALFOSC-FASU

\subsection{Fiber spectra from SDSS survey}
\label{sec2:sdss}

Description about the SDSS project, and the SDSS and BOSS instruments. We use until the SDSS-DR14 version.
